A Spiking Independent Accumulator Model for\\Winner-Take-All Computation

### 2017-07-17 doc/poster/poster.tex
Use vector graphics for logos in poster.
Increase poster font size.

\usepackage[orientation=landscape,size=a0,scale=1.5]{beamerposter}
\usepackage{calc}
\usepackage{commath}
\usepackage[no-math]{fontspec}
\usepackage{mathspec}
\usepackage{nag}
\usepackage{siunitx}
\usepackage{tcolorbox}

@@

                \vspace*{10mm}
                \insertauthor\par\insertinstitute%
            \end{center}
        \end{column}
        \begin{column}{190mm}
            \centering
            % FIXME higher resolution images
            \includegraphics[width=92.8mm]{uw_bow}\hfill
            \includegraphics[width=86.8mm]{CTN_logo}\\\vspace*{10mm}
            \includegraphics[width=187.7mm]{CNRG_BoW}
        \end{column}
        \begin{column}{20mm}
        \end{column}
    \end{columns}
    \vspace*{20mm}

@@

        \begin{tcolorbox}[title=Motivation, add to width=-5cm]

@@

        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=13cm]

@@

                        a_i(t) = G_i\left[a_i e_i x(t) + J_i^{\mathrm{bias}} \right]
                        \text{ and decoding }
                        \hat{x}(t) = \sum_i d_i \left[(a_i * h)(t) \right]

@@

        \begin{tcolorbox}[title=Benchmarks, add to width=-5cm]

@@

        \begin{tcolorbox}[title=Conclusions, add to width=-3cm]

@@

            \raisebox{-0.5\height}{\includegraphics[scale=3]{lca-sketch}}

@@

            \raisebox{-0.5\height}{\includegraphics[scale=3]{ia-sketch}}

>>>>

\usepackage[orientation=landscape,size=a0,scale=1.7]{beamerposter}
\usepackage{calc}
\usepackage{commath}
\usepackage[no-math]{fontspec}
\usepackage{mathspec}
\usepackage{nag}
\usepackage{siunitx}
\usepackage{tcolorbox}

@@

                \vspace*{10mm}
                \insertauthor\par\insertinstitute%
            \end{center}
        \end{column}
        \begin{column}{190mm}
            \centering
            \raisebox{-0.5\height}{\includegraphics[trim=96.65 0 0 0,width=102.8mm]{UniversityOfWaterloo_logo_vert_cmyk}}\hfill
            \raisebox{-0.5\height}{\includegraphics[width=86.8mm]{CTN_logo}}\\
            \includegraphics[width=187.7mm]{cnrg_logo}
        \end{column}
        \begin{column}{20mm}
        \end{column}
    \end{columns}
    \vspace*{20mm}

@@

        \begin{tcolorbox}[title=Motivation, add to width=-2cm]

@@

        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=5cm]

@@

                        $a_i(t) = G_i\left[a_i e_i x(t) + J_i^{\mathrm{bias}} \right]$
                        and decoding
                        $\hat{x}(t) = \sum_i d_i \left[(a_i * h)(t) \right]$

@@

        \begin{tcolorbox}[title=Benchmarks, add to width=-3cm]

@@

        \begin{tcolorbox}[title=Conclusions, add to width=0cm]

@@

            \raisebox{-0.5\height}{\includegraphics[scale=2.9]{lca-sketch}}

@@

            \raisebox{-0.5\height}{\includegraphics[scale=2.9]{ia-sketch}}
